Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
add two figures to the paper
Added screenshots and descriptions for pdf version, outputing index.html vs paper.html and both paper.pdf and index.pdf. need to figure out why pdy-only divs are getting rendered in html

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{End-user Web Scraping For Customization}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can install browser extensions and run
  arbitrary Javascript in the developer console to change them. However,
  this malleability is only accessible to programmers with knowledge of
  HTML, CSS, Javascript and the DOM. To broaden access to customization,
  our prior work developed an approach that empowers end-users to
  customize websites without traditional programming via a browser
  extension called Wildcard. Wildcard's customizations are powered by
  web scraping adapters which are currently written in Javascript by
  programmers. This means that end-users can only customize a website if
  a programmer has written an adapter for it. Furthermore, end-users do
  not have the ability to extend adapters in order to perform new
  customizations or repair adapters to fix broken customizations.

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Chickenfoot
\citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
and Vegemite {[}lin2009{]} help users tweak and adapt websites to fit
their unique requirements, ranging from reorganizing or annotating
content on the website to automating common tasks. In our prior work, we
presented Wildcard \citep{litt2020a}, a customization system which
enables end-users to customize websites through direct manipulation. It
does this by augmenting websites with a table view that shows their
underlying structured data. The table is bidirectionally synchronized
with the original website, so end-users can easily customize the website
by interacting with the table, including sorting and filtering data,
adding annotations, and running computations in a spreadsheet formula
language.

Wildcard has a key limitation. In order to enable end-users to customize
a website, a Javascript programmer first needs to code an adapter that
specifies how to scrape the website content and set up a bidirectional
synchronization with Wildcard's table view. Take Alice, an end-user who
uses Wildcard to customize her experience on Google Scholar as shown
above. Wildcard's sorting customization gives her the power to sort
publications by title which the website does not natively allow. She
thinks this will be useful on Weather.com to sort the ten day forecast
by the weather descriptions so that she can quickly find all the sunny
days. Unfortunately, a programmer has not coded an adapter for
Weather.com so Alice is unable to customize it. Additionally, if the
adapter for Google Scholar stops functioning when the website changes,
Alice has no recourse to repair it on her own.

In this paper, we describe an addition to Wildcard: a system that
enables end-users to create, extend and repair website adapters by
demonstration within the browser. Using this scraping system, an
end-user can perform end-to-end web customizations using Wildcard on
arbitrary websites, without ever needing to code an adapter. Through a
series of examples, we show that end-users can utilize our system to
successfully create Wildcard adapters on a variety of websites via
demonstration (Section~\ref{sec:demos}). We also describe key aspects of
our system and how web scraping for customization reveals a constraint
that simplifies the \emph{wrapper induction} \citep{kushmerick2000} task
used to generalize user demonstrations
(Section~\ref{sec:implementation}).

@@

In this section, we show how end-users can create, extend and repair
adapters for Wildcard via demonstration.

@@

Alice, our end-user from Section~\ref{sec:introduction}, wants to
customize her experience on Weather.com by sorting the ten-day forecast
based on the description of the weather on each day, allowing her to
easily view all the sunny days. She starts the adapter creation process
by clicking a context menu item within the Weather.com page, and hovers
over a data value she might like to scrape.

The system provides live feedback as Alice hovers, demonstrating the
\textbf{live programming} principle:

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row.
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data.
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table.
\end{itemize}

Alice tries hovering over several other elements in the page, taking
advantage of the live feedback environment to decide what data would be
useful. After considering several options, she decides to save the date
field in the first column of the table, and commits the action by
clicking.

Next, she performs a similar process to fill the next column with the
weather descriptions. After filling both columns, she also tries
hovering over previously scraped data, and the toolbar at the top of the
page indicates which column corresponds to the previously scraped data.
Finally, she ends the adapter creation process and is able to
immediately sort the forecast by the weather description column, because
Wildcard provides a \textbf{unified environment} that combines both
scraping and customizing:

@@

Alice has previously used Wildcard to customize timeanddate.com. In
addition to sorting the list of holidays in a year by the day of the
week, she also wants to sort them by category so she can view all the
federal holidays together. Previously, she would have needed to find a
programmer to help her edit the adapter code to incorporate this
additional data, but using our system's support for \textbf{editing by
demonstration}, Alice can extend the adapter herself.

While viewing the website, she clicks the ``Edit Adapter'' button above
the Wildcard table to initiate the adapter editing process. As she
hovers over the currently scraped values, the columns they belong to are
highlighted. Finally, she clicks on ``Federal Holiday'' to add the new
column of data and saves the changes. Alice then proceeds to sort the
list by the type of holiday without the intervention of a programmer.

@@

Alice next visits Google Scholar to look up references for her thesis
project. Unfortunately, the customization she had applied to sort
publications by their title (which is not natively supported by Google
Scholar) is no longer working. In fact, the column in the Wildcard table
that contained all the publication titles is empty, because the
website's internals changed and broke the adapter's scraping logic.
Alice can repair this on her own, again taking advantage of
\textbf{editing by demonstration}.

Alice initiates the editing process, and initially hovers over the
desired value to demonstrate the column she wants to scrape. However,
the \textbf{live programming} interface indicates to her that the values
would be populated into column D; instead, she wants the values to be
inserted into column A where they previously appeared. So, Alice clicks
on the symbol for column A to indicate that she wants to scrape the
values into that column. She then proceeds to re-apply her customization
to the website by sorting the publications by their title without the
intervention of a programmer.

@@

\begin{itemize}
\tightlist
\item
  We generate a single \emph{row selector} for the website: a CSS
  selector that returns a set of DOM elements corresponding to
  individual rows of the table.
\item
  For each column in the table, we generate a \emph{column selector}, a
  CSS selector that returns the element containing the column value
  within that row.
\end{itemize}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\textless{}body\textgreater{}}
    \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
    \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{’container’}\KeywordTok{\textgreater{}}
        \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
            \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}names\textquotesingle{}}\KeywordTok{\textgreater{}}
                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/span\textgreater{}}
                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Tony Stark }\KeywordTok{\textless{}/span\textgreater{}}
            \KeywordTok{\textless{}/div\textgreater{}}
           \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{’gender’}\KeywordTok{\textgreater{}}\NormalTok{ Male }\KeywordTok{\textless{}/span\textgreater{}}
        \KeywordTok{\textless{}/div\textgreater{}}
        \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
            \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}names\textquotesingle{}}\KeywordTok{\textgreater{}}
                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Black Widow }\KeywordTok{\textless{}/span\textgreater{}}
                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Natalia Romanoff }\KeywordTok{\textless{}/span\textgreater{}}
            \KeywordTok{\textless{}/div\textgreater{}}
            \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{’gender’}\KeywordTok{\textgreater{}}\NormalTok{ Female }\KeywordTok{\textless{}/span\textgreater{}}
        \KeywordTok{\textless{}/div\textgreater{}}
\NormalTok{        ...}
    \KeywordTok{\textless{}/div\textgreater{}}
\KeywordTok{\textless{}/body\textgreater{}}
\end{Highlighting}
\end{Shaded}

The user performs a demonstration by clicking on the SPAN element
containing ``Tony Stark.'' Our algorithm traverses upwards from the
demonstrated element, considering each successive parent element as a
potential candidate for the row element. For each parent element \(n\),
the process is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  compute a selector \(s\) that when executed on \(n\) only returns the
  demonstrated element
\item
  for each sibling \(m\) of \(n\), execute \(s\) on \(m\) and record
  whether the selector returned an element. Intuitively, if the selector
  returns an element, this suggests that the sibling \(m\) has some
  parallel structure to \(n\)
\item
  compute \(n_{siblings}\), the number of sibling elements of \(n\) for
  which \(s\) returned an element
\end{enumerate}

Notice how the row-sibling constraint simplifies the problem: row
candidates without siblings that return an element after \(s\) is
executed on them have \(n_{siblings}\) = 0, thus disqualifying them.
Furthermore, a candidate element \(n\) is only accepted as the row
element if the row selector associated with it only matches itself and
elements that are its direct siblings.

From the parent of the initial SPAN element, the algorithm moves up the
DOM tree until it reaches the BODY element. Then, it generates a
selector for each \(n\) and discards any \(n\) with a selector that
matches elements that are either not itself or a direct sibling.
Finally, the algorithm picks an \(n\) with the largest, positive
\(n_{siblings}\), preferring nodes lower in the tree as a tiebreaker.
\(s\) is used as the selector for the column.

Applying this to our example, if the user clicks on the SPAN element
containing ``Tony Stark,'' , the first parent element is the DIV with
the class \emph{names}This DIV has a sibling SPAN element, but the
sibling doesn't return an element when \emph{.super\_hero}, the selector
that identifies the initial SPAN in the DIV, is executed on it. As a
result, it has \(n_{siblings}\) = 0. At the level above that, we
consider the DIV with class \emph{avenger}, which has at least one
sibling that returns an element when the selector \emph{.super\_hero} is
executed on it. Finally, the level above that once again has no siblings
that return an element when the selector \emph{.super\_hero} is executed
on them. Therefore, our algorithm returns the DIV element and outputs
\emph{.avenger} as the row selector and \emph{.super\_hero} as the
column selector. These selectors are used to generate a DOM scraping
adapter which returns the DOM elements corresponding to a superhero data
row in the table.

@@

The row-sibling constraint we mentioned earlier is important for the end
goal of customization because row elements that are not direct siblings
may not represent data on the website that should be related as part of
the same table by customizations such as sorting and filtering. Take the
following sample HTML layout showing two tables of superheros (Team Iron
Man and Team Captain America):

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\textless{}body\textgreater{}}
  \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
  \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{’container’}\KeywordTok{\textgreater{}}
      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/span\textgreater{}}
      \KeywordTok{\textless{}/div\textgreater{}}
      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Black Widow }\KeywordTok{\textless{}/span\textgreater{}}
      \KeywordTok{\textless{}/div\textgreater{}}
\NormalTok{      ...}
  \KeywordTok{\textless{}/div\textgreater{}}
  \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Captain America }\KeywordTok{\textless{}/h1\textgreater{}}
  \KeywordTok{\textless{}div\textgreater{}}
      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Captain America }\KeywordTok{\textless{}/span\textgreater{}}
      \KeywordTok{\textless{}/div\textgreater{}}
      \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
          \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Scarlet Witch }\KeywordTok{\textless{}/span\textgreater{}}
      \KeywordTok{\textless{}/div\textgreater{}}
\NormalTok{      ...}
  \KeywordTok{\textless{}/div\textgreater{}}
\KeywordTok{\textless{}/body\textgreater{}}
\end{Highlighting}
\end{Shaded}

Without the constraint that row elements have to be direct siblings, the
row generalization algorithm could determine the row selector to be
\emph{.avenger} because it matches the largest number of parallel
structures (has the largest \(n_{siblings}\)). While this may be the
correct result for the task of extraction, it is not for the task of
customization. The selector matches all rows across the two tables so
the sorting and filtering customizations could place rows in the
incorrect table and thereby distort what the tables represent. Because
of this, our system currently does not support such DOM structures but
we plan to explore the possibility of extracting multiple tables from a
website and joining them.

Another structure that our system cannot currently generalize over is
one in which column elements are not contained within a row element that
is a direct sibling of all the other row elements. Take the following
sample HTML layout showing a table of superheros:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\textless{}body\textgreater{}}
  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Tony Stark }\KeywordTok{\textless{}/span\textgreater{}}
  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Captain America }\KeywordTok{\textless{}/h1\textgreater{}}
  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Steven Rogers }\KeywordTok{\textless{}/span\textgreater{}}
  \KeywordTok{\textless{}h1}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Black Widow }\KeywordTok{\textless{}/h1\textgreater{}}
  \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Real Name: Natalia Romanoff }\KeywordTok{\textless{}/span\textgreater{}}
\NormalTok{  ...}
\KeywordTok{\textless{}/body\textgreater{}}
\end{Highlighting}
\end{Shaded}

This page contains one table of data in which rows are made up of an H1
tag (super hero name) and a SPAN tag (real name). For the task of
extraction, the DOM elements can be scraped using the shown classes to
output a table in which the values of the H1 tags form the first column
and the values of the SPAN tag form the second column. For the task of
customization, our system would need to know what the row boundaries
were in order for customizations such as sorting and filtering to work
as expected. In Wildcard, this can be done with a hand-coded adapter by
creating artificial row boundaries. In the above DOM structure, an
artificial row boundary could be created by representing a row as an H1
tag and the SPAN tag that immediately follows it. These artificial rows
would form a single unit which would not distort the website after a
sorting or filtering customization. We plan to explore how such
artificial row boundaries might be created via demonstration in order to
support these structures (which are not uncommon, and can be seen, for
example, in HackerNews).

@@

In the previous iteration of Wildcard, web scraping was an entirely
separate activity from customization. Programmers that wrote scraping
adapters would need to switch into an IDE to write code as part of
customizing a new website, making it a much less unified environment.

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, a programming-by-example system for data wrangling,
reported that ``although data scientists were aware of and appreciated
the productivity benefits of existing data wrangling tools, having to
leave their native notebook environment to perform wrangling limited the
usefulness of these tools.'' In web scraping, if a user comes across an
omission while working with data scraped from a website, they need to
switch from the environment in which they are using the data to the
environment in which they wrote their scraping code in order to edit and
re-run it. Sometimes, the divide is more subtle. Vegemite
\citep{lin2009}, a system for end-user programming of mashups, had
separate steps for scraping data from a website and augmenting that data
via automation tasks. During a user study, participants reported that
``it was confusing to use one technique to create the initial table, and
another technique to add information to a new column.''

>>>>

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Towards End-user Web Scraping For Customization}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can install browser extensions and run
  arbitrary Javascript in the developer console to change them. However,
  this malleability is only accessible to programmers with knowledge of
  HTML and Javascript. To broaden access to customization, our prior
  work developed an approach that empowers end-users to customize
  websites without traditional programming via a browser extension
  called Wildcard. However, Wildcard only opened part of the
  customization process to end-users, and still required programmers to
  write site-specific adapters to map website data to a table structure.
  This means that end-users can only customize a website if a programmer
  has written an adapter for it. Furthermore, end-users do not have the
  ability to extend adapters in order to perform new customizations or
  repair adapters to fix broken customizations.

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Chickenfoot
\citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
and Vegemite \citep{lin2009} help users tweak and adapt websites to fit
their unique requirements, ranging from reorganizing or annotating
content on the website to automating common tasks. In our prior work, we
presented Wildcard \citep{litt2020a}, a customization system which
enables end-users to customize websites through direct manipulation. It
does this by augmenting websites with a table view that shows their
underlying structured data. The table is bidirectionally synchronized
with the original website, so end-users can easily customize the website
by interacting with the table, including sorting and filtering data,
adding annotations, and running computations in a spreadsheet formula
language.

Wildcard has a key limitation. In order to enable end-users to customize
a website, a Javascript programmer first needs to code an adapter that
specifies how to scrape the website content and set up a bidirectional
synchronization with Wildcard's table view. Even though programmers can
share adapters with end-users, this means that an end-user can only use
Wildcard on websites where some programmer has already written an
adapter. Additionally, if an adapter doesn't scrape the desired data, or
stops functioning correctly when a website changes, an end-user has no
recourse to extend or repair it on their own.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/overview.png}
  \caption{\label{fig:overview}Our work enables end-users to create Wildcard site adapters by demonstration.}
\end{figure*}

In this paper, we describe an addition to Wildcard: a system that
enables end-users to create, extend and repair website adapters by
demonstration within the browser. Using this scraping system, an
end-user can perform web customizations using Wildcard on arbitrary
websites, without ever needing to code an adapter. Through a series of
examples, we show that our system can create Wildcard adapters on a
variety of websites via demonstration (Section~\ref{sec:demos}). We also
describe key aspects of our system and how web scraping for
customization leads to a constraint that simplifies the \emph{wrapper
induction} \citep{kushmerick2000} task used to generalize user
demonstrations (Section~\ref{sec:implementation}).

@@

In this section, we show how end-users can create, extend and repair
adapters for Wildcard via demonstration.{ These demos are best viewed as
videos in the online version of this paper
(\url{https://kapaya.github.io/px21}).}

@@

Jen wants to customize her experience on Weather.com by sorting the
ten-day forecast based on the description of the weather on each day,
allowing her to easily view all the sunny days. She starts the adapter
creation process by clicking a context menu item within the Weather.com
page, and hovers over a data value she might like to scrape.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/creating.png}
  \caption{\label{fig:creating} Creating an adapter: 1) column data will be scraped into, 2) system's controls, 3) demonstrated column value and row from which colums should be demonstrated from 4) column values determined by generalization algorithm 5) column values populated in table, 6) next column to scrape data into and 7) button to save adapter created by demonstration}
\end{figure*}

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row (1
  in Figure~\ref{fig:creating}).
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data (3 \& 4 in Figure~\ref{fig:creating}).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (5 in Figure~\ref{fig:creating}).
\end{itemize}

Jen tries hovering over several other elements in the page, taking
advantage of the live feedback environment to decide what data would be
useful. After considering several options, she decides to save the date
field in the first column of the table, and commits the action by
clicking.

Next, she performs a similar process to fill the next column with the
weather descriptions. After filling both columns, she also tries
hovering over previously scraped data, and the toolbar at the top of the
page indicates which column corresponds to the previously scraped data.
Finally, she ends the adapter creation process (7 in
Figure~\ref{fig:creating}) and is able to immediately sort the forecast
by the weather description column, because Wildcard provides a
\textbf{unified environment} that combines both scraping and
customizing.

@@

Jen uses Wildcard on timeanddate.com as can be seen from 1 in
Figure~\ref{fig:extending}. In addition to sorting the list of holidays
in a year by the day of the week, she also wants to sort them by
category so she can view all the federal holidays together. Previously,
she would have needed to find a programmer to help her edit the adapter
code to incorporate this additional data, but using our system's support
for \textbf{editing by demonstration}, Jen can extend the adapter
herself.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/extending.png}
  \caption{\label{fig:extending} Extending an adapter: 1) table showing current columns and rows, 2) button for initiating adapter extension process, 3) new column value demonstrated and generalized, 4) new column values in the table and 5) button to save adapter extended by demonstration.}
\end{figure*}

While viewing the website, she clicks the ``Edit Adapter'' button (2 in
Figure~\ref{fig:extending}) above the Wildcard table to initiate the
adapter editing process. As she hovers over the currently scraped
values, the columns they belong to are highlighted. Finally, she clicks
on ``Federal Holiday'' (3 in Figure~\ref{fig:extending}) to add the new
column of data to the table (4 in Figure~\ref{fig:extending}) and saves
the changes (5 in Figure~\ref{fig:extending}). Jen then proceeds to sort
the list by the type of holiday without the intervention of a
programmer.

@@

Jen next visits Google Scholar to look up references for her thesis
project. Unfortunately, the customization she had applied to sort
publications by their title (which is not natively supported by Google
Scholar) is no longer working. In fact, the column in the Wildcard table
that contained all the publication titles is empty (1 in
Figure~\ref{fig:repairing}), because the website's internals changed and
broke the adapter's scraping logic. Jen can repair this on her own,
again taking advantage of \textbf{editing by demonstration}.

Jen initiates the editing process (2 in Figure~\ref{fig:repairing}), and
initially hovers over the desired value to demonstrate the column she
wants to scrape. However, the \textbf{live programming} interface
indicates to her that the values would be populated into column D;
instead, she wants the values to be inserted into column A where they
previously appeared. So, Jen clicks on the symbol for column A (3 in
Figure~\ref{fig:repairing}) to indicate that she wants to scrape the
values into that column and demonstrates the first publication title (4
in Figure~\ref{fig:repairing}). The missing values are now back in the
table (5 in Figure~\ref{fig:repairing}). She then proceeds to save her
changes (6 in fig:repairing) and re-apply her customization to the
website by sorting the publications by their title without the
intervention of a programmer.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/repairing.png}
  \caption{\label{fig:repairing} Repairing an adapter: 1) empty column in table because website changed and adapter can no longer scrape values, 2) button for initiating adapter repair 3) column to scrape data into, 4) missing column value demonstrated and generalized, 5) missing column values back in the table and 6) button to save adapter repaired by demonstration.}
\end{figure*}

@@

\begin{itemize}
\tightlist
\item
  We generate a single \emph{row selector} for the website: a CSS
  selector that returns a set of Document Object Model (DOM) elements
  corresponding to individual rows of the table.
\item
  For each column in the table, we generate a \emph{column selector}, a
  CSS selector that returns the element containing the column value
  within that row.
\end{itemize}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{media/algorithm.png}
  \caption{\label{fig:algorithm}Our system applies a heuristic to identify DOM elements that correspond to rows in the data table.}
\end{figure*}

The user performs a demonstration by clicking on element (a) in
Figure~\ref{fig:algorithm} containing ``Tony Stark.'' Our algorithm
traverses upwards from the demonstrated element, considering each
successive parent element ((b1), (c1) and (d) in
Figure~\ref{fig:algorithm}) as a potential candidate for the row
element. For each parent element \(n\), the process is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  compute a column selector \(s\) that when executed on \(n\) only
  returns the demonstrated element
\item
  for each sibling \(m\) of \(n\), execute \(s\) on \(m\) and record
  whether the selector returned an element. Intuitively, if the selector
  returns an element, this suggests that the sibling \(m\) has some
  parallel structure to \(n\)
\item
  compute \(n_{siblings}\), the number of sibling elements of \(n\) for
  which \(s\) returned an element
\end{enumerate}

Notice how the \emph{row-sibling constraint} simplifies the problem: row
candidates without siblings that return an element after \(s\) is
executed on them ((b1) in Figure~\ref{fig:algorithm}) have
\(n_{siblings}\) = 0, thus disqualifying them. Furthermore, a candidate
element \(n\) is only accepted as the row element if the row selector
\(n_{selector}\) associated with it only matches itself and elements
that are its direct siblings.

The algorithm stops traversing upwards once it reaches the BODY element.
Then, it generates a selector \(n_{selector}\) for each \(n\) and
discards any \(n\) with an \(n_{selector}\) that matches elements that
are either not itself or a direct sibling. Finally, the algorithm picks
an \(n\) with the largest, positive \(n_{siblings}\), preferring nodes
lower in the tree as a tiebreaker. \(n_{selector}\) is used as the
selector for the row and \(s\) is used as the selector for the column.
The row and column selectors are used to generate a scraping adapter
which returns the DOM elements corresponding to a superhero data row in
the table and sets up the bidirectional synchronization.

@@

The row-sibling constraint we mentioned earlier is important for the end
goal of customization because row elements that are not direct siblings
may not represent data on the website that should be related as part of
the same table by customizations such as sorting and filtering.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/limitations.png}
  \caption{\label{fig:limitations} Our generalization algorithm cannot generalize on websites with the shown layouts. The elements with the blue border correspond to rows of the data in each layout respectively.}
\end{figure*}

For \emph{Generalization Limitation 1} shown in
Figure~\ref{fig:limitations}, without the constraint that row elements
have to be direct siblings, the row generalization algorithm could
determine the row selector to be \emph{.avenger} (elements with blue
border in Figure~\ref{fig:limitations}) because it matches the largest
number of parallel structures (has the largest \(n_{siblings}\)). While
this may be the correct result for the task of extraction, it is not for
the task of customization. The selector matches all rows across the two
tables so the sorting and filtering customizations could place rows in
the incorrect table and thereby distort what the tables represent.
Because of this, our system currently does not support such DOM
structures but we plan to explore the possibility of extracting multiple
tables from a website and joining them.

For \emph{Generalization Limitation 2} shown in
Figure~\ref{fig:limitations}, website contains one table of data in
which rows are made up of the alternating H1 and SPAN tags (elements
with blue border in Figure~\ref{fig:limitations}). For the task of
extraction, the DOM elements can be scraped using the shown classes to
output a table in which the values of the H1 tags form the first column
and the values of the SPAN tag form the second column. For the task of
customization, our system would need to know what the row boundaries
were in order for customizations such as sorting and filtering to work
as expected. In Wildcard, this can be done with a hand-coded adapter by
creating artificial row boundaries. In the above DOM structure, an
artificial row boundary could be created by representing a row as an H1
tag and the SPAN tag that immediately follows it. These artificial rows
would form a single unit which would not distort the website after a
sorting or filtering customization. We plan to explore how such
artificial row boundaries might be created via demonstration in order to
support these structures (which are not uncommon, and can be seen, for
example, in HackerNews).

@@

In the previous iteration of Wildcard, web scraping was an entirely
separate activity from customization. Programmers that wrote scraping
adapters would need to switch into an IDE to write code as part of
customizing a new website.

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they wrote their scraping code in order to edit
and re-run it. In web customization, Vegemite \citep{lin2009}, a system
for end-user programming of mashups, reported that participants of its
user study thought ``it was confusing to use one technique to create the
initial table, and another technique to add information to a new
column.'' This hints at the need for a unified environment and a unified
workflow.
